Redundant calibration as a complex optimization problem

### 2016-12-05 paper.tex
started working on abstract, still lots to be done

\title[Unknown]{TBD}
\author[A. V. Raveendran and A. N. Other]{A. V. Raveendran$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
highlight the proper use of \LaTeXe\ code with the class file.
These changes are for illustrative purposes and do not reflect the
original paper by A. V. Raveendran.}\\
$^{1}$Indian Institute of Astrophysics, Bangalore 560034, India\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

\begin{abstract}
TBD
\end{abstract}

>>>>

\title[Unknown]{Redundant calibration as a complex optimization problem}
\author[A. V. Raveendran and A. N. Other]{A. V. Raveendran$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
highlight the proper use of \LaTeXe\ code with the class file.
These changes are for illustrative purposes and do not reflect the
original paper by A. V. Raveendran.}\\
$^{1}$Indian Institute of Astrophysics, Bangalore 560034, India\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

\begin{abstract}
Traditionally redundant calibration is implemented via a layered algorithmic pipeline, i.e. a basic firstcal is performed, followed by LOGCAL and LINCAL.  We first show
that LINCAL is effectively the non-linear least-squares Gauss-Newton algorithm. An easy way to reduce the number of layers that are currently used would therefore be to employ the Levenberg-Marquardt algorithm instead. We further show that instead of splitting our calibration problem into its phase and amplitude components,
which is the avenue taken by LINCAL, we can treat the complex unknown parameters and their complex conjugates as separate unknowns instead.

In this paper we use complex least-squares to perform redundant calibration. Traditionally redundant calibration is performed by splitting the problem into its 
phase and amplitude components, after-which these two components are solved for separately. During complex least-squares, we treat the complex
parameters and their conjugates as independent quantities instead.     
\end{abstract}
